Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-12 rnni_convexity.tex
I'm no longer sure about the lemma. Will have to go through this whole section again...

\begin{lemma}
Let $T = [C_1, \ldots, C_{k-1}, B_{k}, \ldots, B_{n-2}]$ and $R = [C_1, \ldots, C_{k-1}, C_k, \ldots, C_{n-2}]$ be two trees such that $C_k \neq B_k$.
Then there exists exactly one $\rnni$ move on $T$ that results in a tree $T'$ such that $\mrca_{T'}(C_k) < \mrca_{T}(C_k)$.
\label{lemma:mrca_move}
\end{lemma}

>>>>

\begin{lemma}
Let $T = [C_1, \ldots, C_{k-1}, B_{k}, \ldots, B_{n-2}]$ be a tree and $C_k$ a cluster such that $\mrca_T(C_k) > k$.
Then there exists exactly one $\rnni$ move on $T$ that results in a tree $T' = [C_1, \ldots, C_{k-1}, \ldots]$ with $\mrca_{T'}(C_k) < \mrca_{T}(C_k)$.
\label{lemma:mrca_move}
\end{lemma}
